\chapter{Technical Overview}
- As the Introduction has given an overview on the topic itself, why it is important in research and why could be useful in practice,
this chapter does focus on the technologies needed for a Cloud-Federation. \newline
Things to be answered: \newline
- What were the enablers of Cloud Computing? (as a step before Cloud-Federation)
- What has HW/Network/Storage virtualization to do with it?
- What Service Models does Cloud-Computing offer as of today?
- Which research projects are also / have also been following the idea of Cloud-federation?
- What to learn from those research projects?

\section{Enablers of Cloud Computing}
- What allows us to build up a Cloud-Federation?
- Before Cloud-Federation, go into detail about Cloud-Computing, and the technical enablers of this

\subsection{Hardware Virtualization}
- When has it emerged?
- What were the milestones of it?
- Today: CPU virtualization techniques (Intels VT-x, VT-d, VT-c and AMDs IOMMU, etc.)

\subsubsection{Virtualization Types}
- There are several types of Virtualization available. From Software to Hardware accelerated Virtualization.
\begin{itemize}
	\item Full virtualization
	\item Partial virtualization
	\item Paravirtualization
\end{itemize}

\subsubsection{KVM}
- What is KVM?
- Virtualization Type
- How could machines be deployed, cloned, migrated
- Storage pools
- Remote management
- OpenSource
- The Development Part of this MA is using KVM, because...

\subsubsection{XEN}
- What is XEN?
- Virtualization Type
- XEN Domain Model
- OpenSource XEN vs. paid XEN



\subsection{Storage Virtualization}
\subsubsection{Distributed File Systems}
- Tell about location transparency 
Examples: \newline
- Old variant: FTP
- Newer Variants: \newline
- Hadoop Distributed File System (HDFS)
- Amazon S3 File System
- Google File System (GFS)


\subsubsection{Migration}
- Why is Migration important for Clouds? Especially for Cloud-Federation

\subsection{Network Virtualization}
Describe basics of Network Virtualization: 
- Virtualized Data-Layer
- Virtualized Control-Layer


\section{Cloud Computing - Deployment Models}
- Describe Cloud Computing Deployment Models, as these are also of interest for a Cloud-Federation
- Private Clouds should not be able to enter a federation other than a federation that the private Cloud provider established himself (same Company, different locations, same federated Cloud).

\subsection{Public Clouds}

\subsection{Hybrid Clouds}

\subsection{Private Clouds}



\section{Cloud Computing - Service Models}
- Focus on Infrastructure as a Service, as the Cloud-Federation MA will be based on this, however also define the other two Service Models as well.

\subsection{Infrastructure as a Service}

\subsection{Platform as a Service}

\subsection{Software as a Service}



\section{Research Projects on Cloud-Federation}
- These projects were funded by the EU for at least 3 years and have issued Cloud-Federation in their proposals (covering several other topics as well).

\subsection{Contrail}

\subsection{4Caast}

\subsection{Reservoir}