\chapter{Cloud-Federation}
- Second chapter, caring about the implementation part of the MA.
- The Cloud-Federation is seen as an enhancement of the pure Network federation, described in the previous chapter


\section{Agent based Federation}
- Autonomous execution of a generic network-federation
- What aspects could be managed autonomously by agents in pre-federated envionments (pre-federated means: Clouds exist that want to be part of a federation) 

\subsection{Cloud Discovery}
- How to discover Clouds that want to federate?
- What data needs to be exchanged (only for federation information)?

\subsection{Match Making}
- If a Cloud was found that is a good federation partner (decided by the Cloud Discovery Agent), what has to be done prior the upcoming federation?
- Synchronization of sliced OpenFlow Tables, maybe User-Pool synchronization, if Cloud-Federation is not only happening on the Network-Layer

\subsection{Establishing a Federation}
- After a Federation Match was established, go on with the real federation of both Cloud partners.
- How could security be granted here? What data needs to be transmitted, while the federation is in place? 



\section{Cloud-Computing Environments}
- As the Cloud-Federation should (at least in theory) be interoparable with the most used Cloud Environments out there, go a bit into detail about three different environments.
- Where is the difference of each introduced solution?
- Where could Agents be placed, to enhance the given solution with federation functionality?

\subsection{OpenStack}
- Focus on that one, as OpenStack is really an emerging Cloud Environment.

\subsection{OpenNebula}

\subsection{Eucalyptus}
